---
title: "Weight of Fish"
author: "Jaylen Johnson"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight

```{r}
Fish <-read.csv(file="Fish.csv",header=TRUE)
```



## Perch



```{r}
Perch <- filter(Fish, Species=="Perch" )
Perch <- select(Perch, -(Species))
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
The best two regressor model defined by the chart above is the model that is H - W.


```{r}
best.Perch_model <- lm(Weight~Height+Width,data=Perch)
five_elementPerch_model <- lm(Weight~.,data=Perch)
anova(best.Perch_model, five_elementPerch_model)
```

This analysis of variance represents how the Two element model is most likely to be significant.  That is why there is little difference when ocmparing it to the fiive element model.  

## Pike

```{r}
Pike <- filter(Fish, Species=="Pike" )
Pike <- select(Pike, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

```{r}
Pike_best_model <- lm(Weight~.,data=Pike)
summary(Pike_best_model)
Pike_best_2_R_model <- lm(Weight~Length1 + Length3,data=Pike)
```

```{r}
Pike_best_model <- lm(Weight~.,data=Pike)
Pike_best_2_R_model <- lm(Weight~Length1 + Length3,data=Pike)
anova(Pike_best_model, Pike_best_2_R_model)
```
Anova shows that the value is .0 and is comparing both models, the P value is lower than 0.5 and we can conclude it is significant below the .05 level.

## Roach

```{r}
Roach <- filter(Fish, Species=="Roach" )
Roach <- select(Roach, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

```{r}
Roach.best.model <- lm(Weight~Length3+Width,data=Roach)
summary(Roach.best.model)
```

```{r}
Roach.best.model <- lm(Weight~Length3+Width,data=Roach)
five_elementRoach_model <- lm(Weight~.,data=Roach)
anova(Roach.best.model, five_elementRoach_model)
```

Comparing the best Roach model with the Five Element roach model, the comparision reuslts in a p value of .9 the RSS in the 5 element model is slightly smaller but not of a significant difference,  Anova says there is no statistical difference between them. 


## Final Summary Statements






